---
title: <div><b style="color:#004F71">BIKE report constant consumption,</b> <i style="color:#004F71">`r params$thehazardnames_dl`</i></div>

output:
  html_document:
   toc: true
   number_sections: true
   theme: lumen 
   highlight: tango
   fig_width: 12
   fig_height: 8
  
date: "`r format(Sys.time(), '%d.%m.%Y')`"

params: 
  solvedBugs: NA
  data1: NA
  bugsresults: NA
  modelchoice: NA
  factor: NA
  pfactor: NA
  conf_interval1: NA
  selectscale1: NA
  selectdist1: NA
  concen: NA
  consum: NA
  ocdata: NA
  prevdata: NA 
  nf: NA
  food: NA
  hazard: NA
  food_used: NA
  input_modelchoice: NA
  input_modelchoice2: NA
  input_modelchoice3: NA
  units_hazard: NA
  units_food: NA
  nU: NA
  nV: NA
  selectQ_dl: NA
  thehazardnames_dl: NA
  datachoice: NA
  constant.consum: FALSE
  
  
---



<style>
.nav-pills > li > a.active,
.nav-pills > li.active > a,
.nav-pills .nav-link.active {
  background-color: #E6F0FF !important;
  color: #003366 !important;
}


.nav-tabs > li > a.active,
.nav-tabs > li.active > a {
  background-color: #E6F0FF !important;
  color: #003366 !important;
}

</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='asis', fig.retina = 2)

library(knitr)
library(shiny)
library(mvtnorm)
library(DT)
#library(rmarkdown)

constant.consum <- params$constant.consum
if (params$datachoice == 'Food diary' | params$datachoice == 'FFQ')
{constant.consum <- FALSE} else if (params$datachoice == "Constant consumption") 
  {constant.consum <- TRUE}


osdlogsw1 <- params$data1$osdlogsw1
osdlogsw2 <- params$data1$osdlogsw2

Weight <- params$data1$Weight

unit_concen <- params$units_hazard$unit_concen
hazard_concen <- params$units_hazard$hazard_concen

unit_consum <- params$units_food$unit_consum
food_consum <- params$units_food$food_consum


foodnamesused <- params$food_used # instead of input$thefoodnames5
hazardnamesused <- params$thehazardnames_dl # instead of input$thehazardnames5

foodnames<-params$food

# transform the credible interval selected by the user to upper and lower limits:
input_conf_interval <- as.double(params$conf_interval1)
input_upper <- 1-(1-input_conf_interval)/2
input_lower <- (1-input_conf_interval)/2

# selections come from plot 1 selections and apply to all plots below. need to add to Download report page!!!
input_selectdist <- params$selectdist1
input_selectscale <- params$selectscale1  # absolute or logarithmic  

foodindex <- match(foodnamesused,foodnames) # indexing of selected foods in all foods
nfused <- length(foodnamesused)     # number of selected foods
nhused <- length(hazardnamesused) # number of selected hazards
hazardtypes <- params$ocdata$hazardtypes
hazardnames <- params$ocdata$hazardnames
hazardtypesused <- hazardtypes[is.element(hazardnames,hazardnamesused)] # types of selected hazards (chemical/microbiological)
nf <- params$nf   # Calculate the number of foods
nh <- length(hazardnames) # Calculate the number of hazards
nhK <- sum(hazardtypes=='K') # number of chemical hazards
nhM <- sum(hazardtypes=='M') # number of microbiological hazards
hazardnamesK <- hazardnames[hazardtypes=='K'] # chemical hazard names
hazardnamesM <- hazardnames[hazardtypes=='M'] # microbiological hazard names
hazardnamesusedK <- hazardnamesused[hazardtypesused=='K'] # selected che hazard names
hazardnamesusedM <- hazardnamesused[hazardtypesused=='M'] # selected mic hazard names
nhusedK <- length(hazardnamesusedK) # number of che hazards selected
nhusedM <- length(hazardnamesusedM) # number of mic hazards selected
hazardindex <- match(hazardnamesused,hazardnames) # 
hazardindexK <- match(hazardnamesusedK,hazardnamesK) # indexing of selected hazards in all che hazards
hazardindexM <- match(hazardnamesusedM,hazardnamesM) # indexing of selected hazards in all mic hazards

limitexpo <- params$ocdata$limitexpo
limitexpoK <- numeric()
limitexpoM <- numeric()
limitexpoK <- as.numeric(limitexpo[hazardtypes=="K"])
limitexpoM <- as.numeric(limitexpo[hazardtypes=="M"])

Rall <- params$factor  # adjustment factor for concentrations
Pall <- params$pfactor # adjustment factor for prevalences
nU <- params$nU
nV <- params$nV

logcK <- params$data1$logcK #raspberry
logLOQK <- params$data1$logLOQK #green
logLODK <- params$data1$logLODK #Siitepöly
logLOQLimK <- params$data1$logLOQLimK
logLODLimK <- params$data1$logLODLimK
logcM <- params$data1$logcM #raspberry
logLOQM <- params$data1$logLOQM # green
logLODM <- params$data1$logLODM #Siitepöly
logLOQLimM <- params$data1$logLOQLimM
logLODLimM <- params$data1$logLODLimM
nexactK <- params$data1$nexactK
nexactM <- params$data1$nexactM

n_sim <- params$bugsresults$n.sims
muw <- params$bugsresults$muw
sigw <- params$bugsresults$sigw

input_modelchoice <- params$input_modelchoice
input_modelchoice2 <- params$input_modelchoice2
input_modelchoice3 <- params$input_modelchoice3

input_selectQ <- params$selectQ_dl


IDnum <- params$data1$IDnum
nd <- params$data1$nd # number of days reported
nr <- params$data1$nr  	   # number of respondents
logs <- params$data1$logs
logsw <- params$data1$logsw

if(nf==1){
  mus0<- params$solvedBugs$mus0_s
  # ppred <- params$solvedBugs$ppred_s 
  Ss<- params$solvedBugs$Ss_s
  Ss0 <- params$solvedBugs$Ss0_s
  mucK <- params$solvedBugs$mucK_s
  sigcK <- params$solvedBugs$sigcK_s
  pK <- params$solvedBugs$pK_s
  mucM <- params$solvedBugs$mucM_s
  sigcM <- params$solvedBugs$sigcM_s
  pM <- params$solvedBugs$pM_s
  
  if(input_modelchoice=="Independent days"){
    logitp0 <- params$solvedBugs$logitp0_s
    
    if(input_modelchoice2=="Yes"){
      Sp <- params$solvedBugs$Sp_s
    }
  }
  
}
if(nf>1){ 
  mus0 <- params$bugsresults$mus0
  #  ppred <- params$bugsresults$ppred
  Ss <- params$solvedBugs$Ss_m
  Ss0 <- params$solvedBugs$Ss0_m
  mucK <- params$bugsresults$mucK
  sigcK <- params$bugsresults$sigcK
  pK <- params$bugsresults$pK
  mucM <- params$bugsresults$mucM
  sigcM <- params$bugsresults$sigcM
  pM <- params$bugsresults$pM
  
  logitp0 <- params$bugsresults$logitp0
  Sp <- params$solvedBugs$Sp_m
}  

Vs <- numeric() # variances
Vs0 <- numeric() # variances

input_lim = 0.95

theresults <- c("Concentrations","Consumptions","Exposures")

```

```{css style settings}
blockquote {
padding: 0 15px;
margin: 0 0 10px;
font-size: 14px;
border-left: 3px solid #eee;
}




```






------------------------------------------------------------------------

[The report was generated from BIKE shiny app. It includes (i) the results from the MCMC simulations presented as figures and tables for the selected hazard, (ii) short information text for each result, and (iii) the input data. Every figure in this document could be downloaded as a png file by using, e.g., the browser's 'Save image as...' option. All tables have their own download buttons.]{style="color: #004F71;font-size: 14px;"}

------------------------------------------------------------------------


# [**Settings**]{style="color: #004F71"} {.tabset}
[The settings used for the model simulations, and the adjustment factors used in the exposures visualizations are presented in the tables below.]{style="color: #004F71;"}

## [**Model settings**]{style="color: #004F71"}

<br />

::: {.cols style="display: grid; grid-template-columns:  1.5fr 1.5fr; grid-column-gap: 25px;"}
::: col

```{r model-params}

DT::datatable(params$modelchoice, 
              colnames = list(h5(tags$b("Model settings")), h5(tags$b("Selected"))),
              class = "table-border stripe", #c("hover", ),
              extensions = c("Buttons","FixedColumns"),
              options = list(
                dom = "Bt",
                buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span>Excel', title = NULL, 
                                    exportOptions = list(columns = ":visible"),
                                    filename =  paste("Model_settings"))
                ),
                columnDefs = list(list(className = 'dt-right', targets = 1)),
                paging=FALSE,
                searching = FALSE,
                ordering = FALSE
              )
)%>%
  formatStyle("V2",  fontWeight = "bold", fontStyle = "normal")
# formatStyle("V1",  fontWeight = "bold", fontStyle = "normal")

```


```{r food-hazard}

cat('\n\n', "Food types: `", params$food,'`\n\n')

```

------------------------------------------------------------------------
**NOTE:** *In all options, the distribution of consumption amounts is estimated for positive consumption days. The amounts and consumption occurrences are assumed independent so that e.g. consuming something rarely is not correlated with the amount when consumed.*

:::

::: {.col data-latex="{0.4\\textwidth}" style="background-color: #F4F3F2;"}

> <br>
> <b style="color:#D0006F">Consumption model</b>
> <ul><li>No distribution model for consumption, everyone consumes the set amount every day. </li>
> 

> <b style="color:#D0006F">Priors for variances</b>
> <ul><li><b>Tau Gamma</b>, is a conventional choice for the prior of inverse variance.</li>
> <li>The restricted <b>Sigma Uniform</b> prior for standard deviation, is determined from an exaggerated upper bound based on data. (This might be more robust with very small data sample).</li>
</ul>
> <b style="color:#D0006F">Number of MCMC iterations</b>
> <br>
> The number of MCMC simulations affects the Monte Carlo accuracy of the results. It is recommended that several iterations of different lengths are tried to gauge how Monte Carlo error could still affect the results.


:::
:::

<br />
<hr />

## [**Adjustment factors**]{style="color: #004F71"}

Changes in the adjustment factors modify the modelled contamination when calculating exposure. The default values are 1. A factor for **concentrations** should be any positive number. A factor for **prevalence** should be between zero (0) and one (1) to ensure that the multiplication produces a mathematically valid prevalence. The factors allow accounting for food processing effects which may either reduce the prevalence, and/or reduce or increase the concentration. Processing effects may be due to cooking, heating, freezing, washing, peeling, storage, etc. 

<br /> 

```{r adj-factors-concen}

cat('**Concentration factors**')

DT::datatable(params$factor,
              #caption = "Concentration factors",
              class = "cell-border",
              extensions = "Buttons",
              options = list(
                dom = "Bt",
                buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span>Excel', title = NULL, 
                                    exportOptions = list(columns = ":visible"),
                                    filename =  paste("Concentration-factors_exposures"))
                ),
                
                paging=FALSE,
                searching = FALSE,
                ordering = FALSE#,
                #scrollX = TRUE,
                #fixedColumns = TRUE
              )
)%>%
  
  formatStyle(0,  fontWeight = "bold", fontStyle = "normal")
```

<br />

```{r adj-factors-prev}

cat('**Prevalence factors**')

DT::datatable(params$pfactor,
              #caption = "Prevalence factors",
              class = "cell-border",
              extensions = "Buttons",
              options = list(
                dom = "Bt",
                buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span>Excel', title = NULL, 
                                    exportOptions = list(columns = ":visible"),
                                    filename =  paste("Prevalence-factors_exposures"))
                ),
                paging=FALSE,
                searching = FALSE,
                ordering = FALSE#,
                #scrollX = TRUE,
                #fixedColumns = TRUE
              )
)%>%
  
  formatStyle(0,  fontWeight = "bold", fontStyle = "normal")
```

<br />
<hr />

# [**Results**]{style="color: #004F71"}

## [**Figures**]{style="color: #004F71"} {.tabset}

### [**Concentrations**]{style="color: #004F71"}


::: {.cols style="display: grid; grid-template-columns:  2fr 1fr; grid-column-gap: 25px;"}
::: col


```{r, echo=FALSE}


#cat('\n\n', "Food-hazard combination: `", params$thehazardnames1, '` in `', params$thefoodnames1, '`\n\n')
cat('\n', "Confidence interval: `", params$conf_interval1, '`\n')
cat('\n',"Scale: `", params$selectscale1, '`\n')
cat('\n',"Distribution: `", params$selectdist1, '`\n')

```



$Figure$ $1.$ Variability distribution for positive hazard concentrations in food. The uncertainty of the true variability distribution is expressed by plotting a range (e.g. pointwise 95%CI) of probable variability distributions ([**straw color**]{style="color: #CEB888;"}). The uncertainty distribution for mean concentration ([**yellow color**]{style="color: #F7CE3C;"}) and median concentration ([**black color**]{style="color:#343841;"}) are plotted in bold lines. In log-scale, the mean and median are equal. For comparison with data, the raw data are represented as cumulative empirical distribution. For data containing censored concentration values, two empirical distributions are plotted, one with lower bound substitution ([**blueberry color**]{style="color: #004F71;"}) and one with upper bound substitution method ([**raspberry color**]{style="color: #D0006F;"}). These represent the best case and worst case interpretations for censored values. Also, data points are plotted as tick marks on the x-axis, showing exact measurements in [**raspberry color**]{style="color: #D0006F;"}, LOQ-values in [**green color**]{style="color: green;"}, and LOD-values in [**blueberry color**]{style="color: #004F71;"}. Note that the distributions in the figures represent truly positive concentrations, excluding zeros.


```{r, include=FALSE, code= readLines('plotsfunctions.R'), cache=FALSE}

knitr::read_chunk('plotsfunctions.R')

#, 'constantconsumK.R', 'constantconsumM.R'

```




```{r concen-plot, distPlot1_1, fig.show ='hold', out.width="600px", out.height="400px"}



distPlot1_1(input_lim, unit_concen, hazard_concen, input_upper, input_lower, n_sim, input_selectdist, input_selectscale, foodnamesused,
            nfused, foodindex, hazardnamesused, hazardtypesused, nhused, 
            hazardnamesK, hazardnamesM, hazardnamesusedK, hazardnamesusedM,
            nhusedK, nhusedM, hazardindex, hazardindexK, hazardindexM,
            nexactK,nexactM,
            nhK, nf, mucK, sigcK, pK, nhM, mucM, sigcM, pM,
            logcK, logLOQK, logLODK, logLOQLimK, logLODLimK, logcM, logLOQM, logLODM, logLOQLimM, logLODLimM
)


```



:::

::: {.col data-latex="{0.4\\textwidth}" style="background-color: #F4F3F2;"}

> <br>
> **Graphical distributions of concentrations** show the variability distribution of positive hazard concentrations in foods. It is obvious that for some hazards (chemical or microbial) also true zero concentrations may be possible. Hence, the full model is a concentration-prevalence model. Because the hazard prevalence is not a fixed assumption, it is always estimated with some uncertainty bounds. The additional data specifications will determine how the data are interpreted and which model is accordingly used. If concentration data represent only truly “positives”, then estimation of prevalence requires separate prevalence data independently of concentration data, and the prevalence is estimated based on the sample size and the number of positives in the sample. In contrast, if concentration data represents “all” concentrations, including possible true zeros, then it leads to a zero-inflated model which estimates prevalence simultaneously with other parameters for concentration distribution. Separate prevalence data are not used or needed then. In both cases, the plot will always show distributions for positive concentrations and the estimated prevalence with 95%CI in a legend.

:::
:::

<hr />

### [**Consumptions**]{style="color: #004F71"}



::: {.cols style="display: grid; grid-template-columns:  2fr 1fr; grid-column-gap: 25px;"}
::: col

```{r}
#cat('\n\n', "Food: `", params$thefoodnames2, '`\n\n')
#cat('\n', "Confidence interval: `", params$conf_interval1, '`\n')
#cat('\n',"Scale: `", params$selectscale1, '`\n')
#cat('\n',"Distribution: `", params$selectdist1, '`\n')

```

$Figure$ $2.$  Constant consumption amounts shown as pie charts (per bodyweight and absolute).



```{r consum-plot, distPlot2_1, fig.show ='hold', out.width="600px", out.height="400px"}

distPlot2_1(input_lim, food_consum, unit_consum, input_upper, input_lower, n_sim, input_selectdist, input_selectscale, foodnames, foodnamesused, nfused, foodindex,
                        nf, nr, nd,logs, logsw,
                        mus0,muw,logitp0,sigw,Ss,Ss0,constant.consum,Weight,osdlogsw1,osdlogsw2,input_modelchoice
)


```


:::

::: {.col data-latex="{0.4\\textwidth}" style="background-color: #F4F3F2;"}

> <br>
> Constant consumption amounts are shown as pie charts (per bodyweight and absolute). Graphical distributions not available.

:::
:::

<hr />

### [**Exposures**]{style="color: #004F71"}



::: {.cols style="display: grid; grid-template-columns:  2fr 1fr; grid-column-gap: 25px;"}
::: col

```{r}

cat('\n', "Confidence interval: `", params$conf_interval1, '`\n')
cat('\n',"Scale: `", params$selectscale1, '`\n')
cat('\n',"Distribution: `", params$selectdist1, '`\n')

```



$Figure$ $3.$ Variability distribution for mean positive exposures per bodyweight (chemical) or acute positive exposures (microbial). The uncertainty of the true variability distribution of positive exposures is expressed by plotting a range (e.g. pointwise 95%CI) of probable variability distributions ([**straw color**]{style="color: #CEB888;"}). The uncertainty distributions for mean ([**yellow color**]{style="color: #F7CE3C;"}) and median ([**black color**]{style="color: #343841;"}) are plotted in bold lines. The (pseudo)empirical cumulative distribution simulated from bootstrapped data are shown using LB substitution ([**blueberry color**]{style="color: #004F71;"}) and UB substitution ([**raspberry color**]{style="color: #D0006F;"}) method. Note that the distributions in the figures represent truly positive exposures, excluding zeros.

<br />

```{r exposures-plot, distPlot3_1, fig.show ='hold', out.width="600px", out.height="400px"}


distPlot3_1(input_lim, unit_concen, hazard_concen, input_upper, input_lower, n_sim,
                        input_selectdist, input_selectscale, input_modelchoice, input_modelchoice2,
                        foodnamesused, nfused, foodindex, hazardnames,
                        nhused,  hazardnamesusedK, hazardnamesusedM,
                        nhusedK, nhusedM, hazardindexK, hazardindexM, Rall, Pall,nhK,nhM,nf,nr,nd,
                        nexactK, nexactM,
                        logs,logsw,logcK,logLOQK,logLODK,logLOQLimK,logLODLimK, logcM,logLOQM,logLODM,logLOQLimM,logLODLimM,
                        logitp0,mucK,mucM,mus0,muw,pK,pM,sigcK,sigcM,sigw,
                        Ss,Ss0,Sp,Weight,constant.consum,osdlogsw1,osdlogsw2
)



```


:::

::: {.col data-latex="{0.4\\textwidth}" style="background-color: #F4F3F2;"}

> <br>
> For <b>chemical hazards</b>, the distribution of chronic (individual average) exposures is plotted, as population distribution of long-term mean amounts per day per bodyweight, over actually contaminated foods on actual consumption days.
>
> For <b>microbiological hazards</b>, the distribution of acute (individual single day) exposures is plotted, as population distribution of single amounts per day, over actually contaminated foods on actual consumption days. Hence, a single ‘serving’ here means one day consumption. For the microbiological exposures this in fact provides the distribution of expected values (which could be decimal numbers) of doses in the contaminated servings if consumed. The actual dose in a random serving would result as a random bacteria count from Poisson distribution that has such expected dose as the parameter.
>
> **A variability distribution** aims to describe how the positive exposure is distributed in the whole population of actual consumers. Therefore, the graphical image shows the worst case exposure that would result if all servings of the food were contaminated and the food was consumed daily. The legend box describes numerically how often the exposure happens.

:::
:::

<hr />


### [**MCMC samples of parameters**]{style="color: #004F71"}{.tabset .tabset-pills}

[**Concentration parameters**]{style="color: #004F71"}

::: {.cols style="display: grid; grid-template-columns:  2fr 1fr; grid-column-gap: 25px;"}
::: col

$Figure$ $4.$ Permuted MCMC samples of model parameters $mu$ and $sigma$ of the log-normal ($mu$, $sigma$)-distribution, and prevalence $q$ of the **hazard**. For each parameter, also the approximated marginal probability density is shown.

<br />


```{r concen-params-plot, distPlot5_1, fig.show ='hold', out.width="600px", out.height="400px"}

#cat('**Concentration parameters**')

distPlot5_1(n_sim, foodnamesused, nfused, foodindex, 
                        hazardnamesusedK, hazardnamesusedM, nhusedK, nhusedM,
                        hazardindexK, hazardindexM,nf,nhK,nhM,
                        nexactK, nexactM,
                        mucK,mucM,pK,pM,sigcK,sigcM
)


```


:::

::: {.col data-latex="{0.4\\textwidth}" style="background-color: #F4F3F2;"}

> <br>
> The posterior distribution is computed using **Markov Chain Monte Carlo (MCMC)** sampling. In MCMC, each iteration step depends on the values generated at the previous step. This sampling converges to the correct target distribution which is the posterior distribution of all unknown parameters. In difficulties, the posterior may be nearly flat or with multiple peaks. This, and/or insufficient iterations may then result into poor convergence, and the obtained parameter estimates would not be valid. Poor convergence and poor mixing of the algorithm could be detected as instability in the parameter distributions. The MCMC sample of the parameters, and the marginal posterior distribution are provided for critical inspection. Although a visual inspection is informal and indicative, it can reveal problems in MCMC sampling. The sample should look smoothly scattered without clustering at some values only. The marginal probability density (plotted on top) should look smooth without ‘extra bumps’. New or increased MCMC runs should lead to same results. If a possible problem is detected, increase MCMC iterations and/or investigate whether there are simply insufficient data for the parameter to be well estimated. Note also that the full joint distribution is a multidimensional distribution which cannot be pictured and these plots only show marginal one-dimensional distributions for each parameter, like shadows of the multidimensional distribution. The parameter samples can be viewed for the concentration distributions. The values at the peaks of those distributions could also be compared with the corresponding parameter estimates directly evaluated from raw (log-)data, e.g., mean and standard deviation, although censored data can make direct comparison less straightforward.

:::
:::

<br>
<hr />



## [**Tables**]{style="color: #004F71"}{.tabset}


[**Posterior predictive distributions**]{style="color: #004F71"}

Posterior predictive distributions present predictions where all uncertainties and variabilities are integrated into one single probability distribution. This can be a useful summary for assessing what is now probable, given all the data with all its variability and uncertainties. The distribution is obtained by averaging (weighing) the possible variability distributions over the uncertainty distribution of their parameters.



```{r, include=FALSE, code= readLines('tablefunctions.R'), cache=FALSE}

knitr::read_chunk('tablefunctions.R')

```




```{r summary-table, echo = F}

# create data frame containing posterior predictive summaries----

resultValues <- table1(n_sim, input_modelchoice,input_modelchoice2,input_modelchoice3,input_modelchoice4,input_modelchoice5,
                   theresults, foodnamesused, nfused, foodindex, hazardnames, 
                   hazardnamesusedK,hazardnamesusedM, nhusedK, nhusedM, hazardindexK, hazardindexM,
                   Rall, Pall,nhK,nhM,nf,nexactK,nexactM,
                   mucK,mucM,mus0,muw,pK,pM,sigcK,sigcM,sigw,
                   logitp0,
                   Ss,Ss0,Sp,constant.consum,logsw,logs,osdlogsw1,osdlogsw2)

datatable(resultValues, rownames = FALSE,
          caption = "POSTERIOR PREDICTIVE DISTRIBUTION SUMMARIES",
          class = 'row-border stripe',
          extensions = c("Buttons", "RowGroup"),
          options = list(
            rowGroup = list(dataSrc = 1), # row grouping feature -> grouped by second column value
            #selection = 'none',
            dom = "Bfrtip",
            buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span> Excel', title = NULL,
                                exportOptions = list(columns = ":visible"),
                                filename =  paste("Posterior_predictive_distribution_summaries"))
            ),
            ## All results appear on same page:
            paging=FALSE, scrollY = "480px"
          )
)

```

<br />

<hr />



# [**Input data**]{style="color:  #004F71"}{.tabset}

<br /> [The following tables contain the input data used for the model simulations. Each table could be downloaded and saved as an Excel file. Note that currently the NAs from the original data are saved as empty cells.]{style="color: #004F71;"} <br />

## [**Concentrations data**]{style="color: #004F71"}

```{r concentab, echo = F}


datatable(params$concen, 
          # colnames = list(h5("Model parameter"), h5("Selected")),
          class = "hover",
          rownames = FALSE,
          extensions = c("Buttons","FixedColumns"),
          options = list(
            dom = "Bt",
            buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span> Excel', title = NULL, 
                                exportOptions = list(columns = ":visible"),
                                filename =  paste("Concentrations_data"))
            ),
            paging=FALSE,
            searching = FALSE,
            ordering = FALSE,
            scrollX = TRUE, scrollY = "400px"
          )
)


```

## [**Consumptions data**]{style="color: #004F71"}

```{r consumtab, echo = F}


datatable(params$consum, 
          # colnames = list(h5("Model parameter"), h5("Selected")),
          class = "hover",
          rownames = FALSE,
          extensions = c("Buttons","FixedColumns"),
          options = list(
            dom = "Bt",
            buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span> Excel', title = NULL, 
                                exportOptions = list(columns = ":visible"),
                                filename =  paste("Consumptions_data"))
            ),
            paging=FALSE,
            searching = FALSE,
            ordering = FALSE,
            scrollX = TRUE, scrollY = "400px"
          )
)


```

## [**Occurrance data**]{style="color: #004F71"}

```{r ocdatatab, echo = F}


datatable(params$ocdata, 
          # colnames = list(h5("Model parameter"), h5("Selected")),
          class = "hover",
          rownames = FALSE,
          extensions = c("Buttons","FixedColumns"),
          options = list(
            dom = "Bt",
            buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span> Excel', title = NULL, 
                                exportOptions = list(columns = ":visible"),
                                filename =  paste("Occurrance_data"))
            ),
            paging=FALSE,
            searching = FALSE,
            ordering = FALSE,
            scrollX = TRUE, scrollY = "400px"
          )
)


```

## [**Prevalence data**]{style="color: #004F71"}

```{r prevdatatab, echo = F}


datatable(params$prevdata, 
          # colnames = list(h5("Model parameter"), h5("Selected")),
          class = "hover",
          rownames = FALSE,
          extensions = c("Buttons","FixedColumns"),
          options = list(
            dom = "Bt",
            buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span> Excel', title = NULL, 
                                exportOptions = list(columns = ":visible"),
                                filename =  paste("Prevalence_data"))
            ),
            paging=FALSE,
            searching = FALSE,
            ordering = FALSE,
            scrollX = TRUE, scrollY = "400px"
          )
)


```

<br>


