---
title: <div><b style="color:#004F71">BIKE report FFQ</b></div>

output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: lumen 
    highlight: tango
    
date: "`r format(Sys.time(), '%d.%m.%Y')`"

runtime: shiny

params: 
  data1: NA
  bugsresults: NA
  bugsresultsls: NA
  plot1: NA 
  plot2: NA
  plot3: NA
  plot4: NA
  plot51: NA
  plot52: NA
  plot6: NA
  plot7: NA
  resultValues: NA
  resultProbs: NA
  modelchoice: NA
  factor: NA
  pfactor: NA
  thefoodnames1: NA
  thehazardnames1: NA
  thefoodnames2: NA
  thefoodnames21: NA
  thefoodnames22: NA
  thefoodnames3: NA
  thehazardnames3: NA
  thefoodnames4: NA
  thehazardnames4: NA
  thefoodnames5: NA
  thefoodnames52: NA
  thehazardnames5: NA
  conf_interval1: NA
  conf_interval2: NA
  conf_interval3: NA
  selectscale1: NA
  selectscale2: NA
  selectscale3: NA
  selectscale4: NA
  selectdist1: NA
  selectdist2: NA
  selectdist3: NA
  concen: NA
  consum: NA
  ocdata: NA
  prevdata: NA 
  nf: NA
  food: NA
  hazard: NA
  nU: NA
  nV: NA
  input_selectQ: NA

  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(shiny)
library(tidyverse)
library(shinyjs)
library(DT)
library(rmarkdown)

```

```{css style settings, echo = FALSE}
blockquote {
    padding: 0 15px;
    margin: 0 0 10px;
    font-size: 14px;
    border-left: 3px solid #eee;
}
```


------------------------------------------------------------------------

[The report was generated from BIKE shiny app. It includes (i) only the results that are visualized in the app after the latest view selections (i.e., figures that have not been visualized in the app are not visible in this document), (ii) short information text for each result, and (iii) the input data. Every figure in this document could be downloaded as a png file by using, e.g., the browser's 'Save image as...' option. All tables have their own download buttons.]{style="color: #D0006F;font-size: 14px;"}

------------------------------------------------------------------------

# [**Settings**]{style="color: #004F71"}
[The settings used for the model simulations, and the adjustment factors used in the exposures visualizations are presented in the tables below.]{style="color: #004F71;"}

## [Model settings]{style="color: #004F71"}

<br />

::: {.cols style="display: grid; grid-template-columns:  1.4fr 1.6fr; grid-column-gap: 25px;"}
::: col

```{r model-params, echo = F, results='asis'}

DT::datatable(params$modelchoice, 
              colnames = list(h5(tags$b("Model settings")), h5(tags$b("Selected"))),
              class = "table-border stripe", #c("hover", ),
              extensions = c("Buttons","FixedColumns"),
              options = list(
               dom = "Bt",
                buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span>Excel', title = NULL, 
                                    exportOptions = list(columns = ":visible"),
                                    filename =  paste("Model_settings"))
                ),
                columnDefs = list(list(className = 'dt-right', targets = 1)),
                paging=FALSE,
                searching = FALSE,
                ordering = FALSE
              )
    )%>%
      formatStyle("V2",  fontWeight = "bold", fontStyle = "normal")
     

```


```{r food-hazard, echo = F, results='asis'}

cat('\n\n', "Food types: `", params$food,'`\n\n')
cat('\n\n', "Hazards: `", params$hazard,'`\n\n')

```

------------------------------------------------------------------------
**NOTE:** *In all options, the distribution of consumption amounts is estimated for positive consumption days. The amounts and consumption occurrences are assumed independent so that e.g. consuming something rarely is not correlated with the amount when consumed.*

:::

::: {.col data-latex="{0.4\\textwidth}" style="background-color: #F4F3F2;"}

> <br>
> <b style="color:#D0006F">Consumption model for FFQ data.</b>
> <br>
> <b>FFQ model</b> assumes every individual has reported mean consumption per day for each food type 
 (zero represents a true non-consumer of the food). Hence, the distribution of mean amounts is estimated for the population of true consumers, along with the proportion of true consumers in the population. Variation between days (or servings) cannot be modeled. Only the assessment of long term ('chronic') consumption is possible.
> <ul><li><b>Mean serving sizes</b>
> With several food types, correlations may be allowed between **daily mean** (log) consumption amounts of different foods, but the correlation parameters are not individual specific (this would require much more reporting days per each individual).
</li>
</ul>
> <b style="color:#D0006F">Priors for variances.</b>
> <ul><li><b>Tau Gamma</b>, is a conventional choice for the prior of inverse variance.</li>
> <li>The restricted <b>Sigma Uniform</b> prior for standard deviation, is determined from an exaggerated upper bound based on data. (This might be more robust with very small data sample).</li>
</ul>
> <b style="color:#D0006F">Number of MCMC iterations.</b>
> <br>
> The number of MCMC simulations affects the Monte Carlo accuracy of the results. It is recommended that several iterations of different lengths are tried to gauge how Monte Carlo error could still affect the results.

:::
:::

<br />
<hr />

## [Adjustment factors]{style="color: #004F71; bold"}

Changes in the adjustment factors modify the modelled contamination when calculating exposure. The default values are 1. A factor for **concentrations** should be any positive number. A factor for **prevalence** should be between zero (0) and one (1) to ensure that the multiplication produces a mathematically valid prevalence. The factors allow accounting for food processing effects which may either reduce the prevalence, and/or reduce or increase the concentration. Processing effects may be due to cooking, heating, freezing, washing, peeling, storage, etc. 

<br /> 

```{r adj-factors-concen, echo = F, results='asis'}

cat('**Concentration factors**')

DT::datatable(params$factor,
              
              class = "cell-border",
              extensions = "Buttons",
              options = list(
                dom = "Bt",
                buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span>Excel', title = NULL, 
                                    exportOptions = list(columns = ":visible"),
                                    filename =  paste("Concentration-factors_exposures"))
                ),
                
                paging=FALSE,
                searching = FALSE,
                ordering = FALSE#,
                
              )
    )%>%
      
      formatStyle(0,  fontWeight = "bold", fontStyle = "normal")
```

<br />

```{r adj-factors-prev, echo = F, results='asis'}

cat('**Prevalence factors**')

DT::datatable(params$pfactor,
              
              class = "cell-border",
              extensions = "Buttons",
              options = list(
                dom = "Bt",
                buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span>Excel', title = NULL, 
                                    exportOptions = list(columns = ":visible"),
                                    filename =  paste("Prevalence-factors_exposures"))
                ),
                paging=FALSE,
                searching = FALSE,
                ordering = FALSE#,
                
              )
    )%>%
      
      formatStyle(0,  fontWeight = "bold", fontStyle = "normal")
```

<br />
<hr />

# [**Results**]{style="color: #004F71"}

## [Figures]{style="color: #004F71"}

### [**Concentrations**]{style="color: #004F71; bold"}

<br />

::: {.cols style="display: grid; grid-template-columns:  2fr 1fr; grid-column-gap: 25px;"}
::: col

```{r concen-plot, echo=FALSE, results='asis', dev = "png", fig.dim = c(12, 8), fig.align = 'left'}





cat('\n\n', "Food-hazard combination: `", params$thehazardnames1, '` in `', params$thefoodnames1, '`\n\n')
cat('\n', "Confidence interval: `", params$conf_interval1, '`\n')
cat('\n',"Scale: `", params$selectscale1, '`\n')
cat('\n',"Distribution: `", params$selectdist1, '`\n')


if (is.null(params$plot1)){cat('**The plot was not generated in the app.**')} else
{params$plot1}


```

<br />

$Figure$ $1.$ Variability distribution for positive hazard concentrations in food. The uncertainty of the true variability distribution is expressed by plotting a range (e.g. pointwise 95%CI) of probable variability distributions ([**straw color**]{style="color: #CEB888;"}). The uncertainty distribution for mean concentration ([**yellow color**]{style="color: #F7CE3C;"}) and median concentration ([**black color**]{style="color:#343841;"}) are plotted in bold lines. In log-scale, the mean and median are equal. For comparison with data, the raw data are represented as cumulative empirical distribution. For data containing censored concentration values, two empirical distributions are plotted, one with lower bound substitution ([**blueberry color**]{style="color: #004F71;"}) and one with upper bound substitution method ([**raspberry color**]{style="color: #D0006F;"}). These represent the best case and worst case interpretations for censored values. Also, data points are plotted as tick marks on the x-axis, showing exact measurements in [**raspberry color**]{style="color: #D0006F;"}, LOQ-values in [**green color**]{style="color: green;"}, and LOD-values in [**blueberry color**]{style="color: #004F71;"}. Note that the distributions in the figures represent truly positive concentrations, excluding zeros.
:::

::: {.col data-latex="{0.4\\textwidth}" style="background-color: #F4F3F2;"}

> <br>
> **Graphical distributions of concentrations** show the variability distribution of positive hazard concentrations in foods. It is obvious that for some hazards (chemical or microbial) also true zero concentrations may be possible. Hence, the full model is a concentration-prevalence model. Because the hazard prevalence is not a fixed assumption, it is always estimated with some uncertainty bounds. The additional data specifications will determine how the data are interpreted and which model is accordingly used. If concentration data represent only truly “positives”, then estimation of prevalence requires separate prevalence data independently of concentration data, and the prevalence is estimated based on the sample size and the number of positives in the sample. In contrast, if concentration data represents “all” concentrations, including possible true zeros, then it leads to a zero-inflated model which estimates prevalence simultaneously with other parameters for concentration distribution. Separate prevalence data are not used or needed then. In both cases, the plot will always show distributions for positive concentrations and the estimated prevalence with 95%CI in a legend.

:::
:::

<hr />

### [**Consumptions**]{style="color: #004F71; bold"}

<br />

::: {.cols style="display: grid; grid-template-columns:  2fr 1fr; grid-column-gap: 25px;"}
::: col
```{r consum-plot, echo = F, results='asis', dev = "png",fig.dim = c(12, 8)}


cat('\n\n', "Food: `", params$thefoodnames2, '`\n\n')
cat('\n', "Confidence interval: `", params$conf_interval2, '`\n')
cat('\n',"Scale: `", params$selectscale2, '`\n')
cat('\n',"Distribution: `", params$selectdist2, '`\n')


if (is.null(params$plot2)){cat('**The plot was not generated in the app.**')} else
{params$plot2}



```

<br />

$Figure$$2a$ Variability distributions for both mean consumptions per bodyweight and mean consumptions in absolute amounts. The uncertainty of the true variability distribution of mean consumptions is expressed by plotting a range (e.g. pointwise 95%CI) of probable variability distributions ([**straw color**]{style="color: #CEB888;"}). The uncertainty distributions for mean ([**yellow color**]{style="color: #F7CE3C;"}) and median ([**black color**]{style="color: #343841;"}) of the distributions are plotted in bold lines. Observed data for reported mean consumptions (from FFQ) are shown as [**raspberry color**]{style="color: #D0006F;"} ticks and the empirical cumulative distribution in [**raspberry color**]{style="color: #D0006F;"} line. Note that a reported zero mean consumption is assumed to represent true non-consumer of the food.
:::

::: {.col data-latex="{0.4\\textwidth}" style="background-color: #F4F3F2;"}

> <br>
> **Graphical distributions for consumptions** of single food types represent the variability distribution of mean consumption per day (per bodyweight or absolute). The proportion of population consuming each food type is estimated based on proportion of non-zero reported mean consumptions in FFQ data. Reported zero mean consumption is assumed to represent a true non-consumer.

:::
:::

<br />

#### [**Serving correlations**]{style="color: #004F71; bold"}
::: {.cols style="display: grid; grid-template-columns:  2fr 1fr; grid-column-gap: 25px;"}
::: col


<br />

```{r correl-plot2, echo = F, results='asis', dev = "png",fig.dim = c(12, 8)}

if (length(params$thefoodnames22)<2 | is.null(params$plot7)){cat('**Requires at least two food types!**')} else {params$plot7}


```

<br />

$Figure$ $2b$ Pairwise scatter plots of logarithms of mean positive consumptions per bodyweights. Data points ([**blueberry color**]{style="color: #004F71;"}) and model based simulations ([**raspberry color**]{style="color: #D0006F;"}). 
:::

::: {.col data-latex="{0.4\\textwidth}" style="background-color: #F4F3F2;"}

> <br>
> The food consumption model contains **one correlation structure** for mean log-consumption amounts for food types. Correlations are not specific per each individual consumer, but generally for the whole group of consumers. The model aims to capture all such pairwise correlations in the consumer population if there are any. The correlation model (if used) is always running for the full set of foods in the data even if only some food types were selected for viewing results. Correlation model for actual daily consumptions is not possible with FFQ data which reports only mean consumptions.

:::
:::

<hr />

### [**Exposures**]{style="color: #004F71; bold"}

<br />

::: {.cols style="display: grid; grid-template-columns:  2fr 1fr; grid-column-gap: 25px;"}
::: col
```{r exposures-plot, echo = F, results='asis', dev = "png",fig.dim = c(12, 8)}


cat('\n\n', "Food-hazard combination: `", params$thehazardnames3, '` in `', params$thefoodnames3, '`\n\n')
cat('\n', "Confidence interval: `", params$conf_interval3, '`\n')
cat('\n',"Scale: `", params$selectscale3, '`\n')
cat('\n',"Distribution: `", params$selectdist3, '`\n')


if (is.null(params$plot3)){cat('**The plot was not generated in the app.**')} else
{params$plot3}

```

<br />

$Figure$ $3$ Variability distribution for mean exposures per bodyweight or as absolute. The uncertainty of the true variability distribution of mean exposures is expressed by plotting a range (e.g. pointwise 95%CI) of probable variability distributions ([**straw color**]{style="color: #CEB888;"}). The uncertainty distributions for mean ([**yellow color**]{style="color: #F7CE3C;"}) and median ([**black color**]{style="color: #343841;"}) are plotted in bold lines. The (pseudo)empirical cumulative distribution simulated from bootstrapped data are shown using LB substitution ([**blueberry color**]{style="color: #004F71;"}) and UB substitution ([**raspberry color**]{style="color: #D0006F;"}) method.
:::

::: {.col data-latex="{0.4\\textwidth}" style="background-color: #F4F3F2;"}

> <br>
> The distribution of chronic (individual average) exposures is plotted, as population distribution of long-term mean amounts per day per bodyweight, or as absolute.
>
> **A variability distribution** aims to describe how the mean exposure is distributed in the whole population of actual consumers. The legend box describes numerically the proportion of consumers in the population.

:::
:::

<hr />

### [**Quantiles**]{style="color: #004F71; bold"}

<br />

::: {.cols style="display: grid; grid-template-columns:  2fr 1fr; grid-column-gap: 25px;"}
::: col

```{r quantiles-plot, echo = F, results='asis', dev = "png",fig.dim = c(12, 8), fig.cap=""}

cat('\n\n', "Food-hazard combination: `",params$thehazardnames4, '` from `', params$thefoodnames4, '`\n\n')
cat('\n',"Scale: `", params$selectscale4, '`\n')
cat('\n',"Total exposure quantile (Q%): `", params$input_selectQ, '`\n')
cat('\n',"Variability sample size for Q%: `", params$nV, '`\n')
cat('\n',"Uncertainty sample size for Q%: `", params$nU, '`\n')


if (params$input_selectQ == "None" | is.null(params$plot4)){cat('**Total exposure quantile is not selected!**')} else {params$plot4}

```

<br />

$Figure$ $4$ Cumulative distributions for separation of uncertainty and variability for mean exposures per bodyweight or as absolute. The uncertainty of true variability distribution of mean exposures summed from all selected foods is expressed by plotting a sample of probable variability distributions ([**raspberry color**]{style="color: #D0006F;"}). The uncertainty distribution for the selected variability quantile is shown between vertical bars (and is subject to Monte Carlo error of 2D simulations).

:::

::: {.col data-latex="{0.4\\textwidth}" style="background-color: #F4F3F2;"}

> <br>
> The total exposure will be computed as the summed exposure from the selected foods. From the distribution of total exposure, a selected quantile point is estimated. The calculations employ 2D simulations (often computationally heavy). BIKE estimates **the quantile for two exposure distributions**: **(a) True consumers only** To evaluate total exposure from several foods, exposures are summed over the selected foods. Note that this corresponds to population of true consumers. The variation of such total exposures is simulated to obtain a distribution for which the selected quantile point is estimated with 95% uncertainty bounds, and **(b) Exposures for whole population (including non-consumers)** The figure that appears in quantile plots shows a plot representing the variability distribution of total exposures of true consumers only (as explained above). However, the quantiles for the overall total exposure distribution, including non-consumers are nevertheless evaluated and numerically given in the other legend in the same figure, accounting for the proportion of consumers of each food.

:::
:::

<br>
<hr />

### [**MCMC samples of parameters**]{style="color: #004F71; bold"}

<br />

::: {.cols style="display: grid; grid-template-columns:  2fr 1fr; grid-column-gap: 25px;"}
::: col

```{r concen-params-plot, echo = F, results='asis', dev = "png", fig.dim = c(12, 8)}

cat('**Concentration parameters**')

cat('\n\n', "Food-hazard combination: `",params$thehazardnames5, '` in `', params$thefoodnames5, '`\n\n')

if (is.null(params$plot51)){cat('**The plot was not generated in the app.**')} else
{params$plot51}
```

<br />

$Figure$ $5a$ Permuted MCMC samples of model parameters $mu$ and $sigma$ of the log-normal ($mu$, $sigma$)-distribution, and prevalence $q$ of the **hazard**. For each parameter, also the approximated marginal probability density is shown.

------------------------------------------------------------------------

```{r consum-params-plot, echo = F, results='asis', dev = "png", fig.dim = c(12, 8) }

cat('**Consumption parameters**')

cat('\n\n', "Food: `",params$thefoodnames52, '`\n\n')

if (is.null(params$plot52)){cat('**The plot was not generated in the app.**')} else
{params$plot52}
```

<br />

$Figure$ $5b$ Permuted MCMC samples of model parameters $mu$ and $sigma$ of the log-normal ($mu$, $sigma$)-distribution, and proportion of consumers $p$ of the **food** in population. For each parameter, also the approximated marginal probability density is shown.

:::

::: {.col data-latex="{0.4\\textwidth}" style="background-color: #F4F3F2;"}

> <br>
> The posterior distribution is computed using **Markov Chain Monte Carlo (MCMC)** sampling. In MCMC, each iteration step depends on the values generated at the previous step. This sampling converges to the correct target distribution which is the posterior distribution of all unknown parameters. In difficulties, the posterior may be nearly flat or with multiple peaks. This, and/or insufficient iterations may then result into poor convergence, and the obtained parameter estimates would not be valid. Poor convergence and poor mixing of the algorithm could be detected as instability in the parameter distributions. The MCMC sample of the parameters, and the marginal posterior distribution are provided for critical inspection. Although a visual inspection is informal and indicative, it can reveal problems in MCMC sampling. The sample should look smoothly scattered without clustering at some values only. The marginal probability density should look smooth without ‘extra bumps’. New or increased MCMC runs should lead to same results. If a possible problem is detected, increase MCMC iterations and/or investigate whether there are simply insufficient data for the parameter to be well estimated. Note also that the full joint distribution is a multidimensional distribution which cannot be pictured and these plots only show marginal one-dimensional distributions for each parameter, like shadows of the multidimensional distribution. The parameter samples can be viewed for both the concentration distributions and consumption distributions. The values at the peaks of those distributions could also be compared with the corresponding parameter estimates directly evaluated from raw (log-)data, e.g., mean and standard deviation, although censored data can make direct comparison less straightforward.

:::
:::

<hr />


## [Tables]{style="color: #004F71"}


### [**Posterior predictive distributions**]{style="color: #004F71"}

Posterior predictive distributions present predictions where all uncertainties and variabilities are integrated into one single probability distribution. This can be a useful summary for assessing what is now probable, given all the data with all its variability and uncertainties. The distribution is obtained by averaging (weighing) the possible variability distributions over the uncertainty distribution of their parameters.


```{r summary-table, echo = F}

datatable(params$resultValues, rownames = FALSE,
          caption = "POSTERIOR PREDICTIVE DISTRIBUTION SUMMARIES",
                    class = 'row-border stripe',
                    extensions = c("Buttons", "RowGroup"),
                    options = list(
                      rowGroup = list(dataSrc = 1), # row grouping feature -> grouped by second column value 
                      
                      dom = "Bfrtip",
                      buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span> Excel', title = NULL, 
                                          exportOptions = list(columns = ":visible"),
                                          filename =  paste("Posterior_predictive_distribution_summaries"))
                      ),
                      
                      paging=FALSE, scrollY = "480px"
                    )
      )
            
```

<br /> <br />

<hr />

### [**Exposure limit analysis**]{style="color: #004F71"}

Exposure limit analysis presents the part of the population (1 = 100%) with exposure below the limit given in the Occurrence dataset. The estimate is given for whole population and for consumers only. The exposure limit can be set as a health based guidance value, for example tolerable daily intake TDI. Note that the exposure calculated by BIKE is in units per day (per bodyweight or as absolute), and thus a health based guidance value given in units per a longer time period  should be adjusted  to units per day before uploading data.

The columns Q05, Q50, Q95 refer to uncertainty quantiles for the 'Quantity' in first column. The 'Quantity' Q95(exposure) refer to the unknown quantiles of variability distribution. This becomes estimated with the indicated uncertainty quantiles Q05, Q50, Q95.



```{r limits-table, echo = F}

datatable(params$resultProbs, rownames = FALSE,
          caption = "Exposure limit analysis",
                    class = 'row-border stripe',
                    extensions = c("Buttons", "RowGroup"),
                    options = list(
                      rowGroup = list(dataSrc = 0), # row grouping feature -> grouped by second column value 
                      
                      dom = "Bfrtip",
                      buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span> Excel', title = NULL, 
                                          exportOptions = list(columns = ":visible"),
                                            filename =  paste("Exposure_limit_analysis"))
                      ),
                      
                      paging=FALSE, scrollY = "480px"
                    )
      )
            
```

<br /> <br />

<hr />

# [**Input data**]{style="color:  #004F71"}

<br /> [The following tables contain the input data used for the model simulations. Each table could be downloaded and saved as an Excel file. Note that currently the NAs from the original data are saved as empty cells.]{style="color: #004F71;"} <br />

## [Concentrations data]{style="color: #004F71; bold"}

```{r concentab, echo = F}

datatable(params$concen, 
             
              class = "hover",
          rownames = FALSE,
              extensions = c("Buttons","FixedColumns"),
              options = list(
                dom = "Bt",
                buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span> Excel', title = NULL, 
                                    exportOptions = list(columns = ":visible"),
                                    filename =  paste("Concentrations_data"))
                ),
                paging=FALSE,
                searching = FALSE,
                ordering = FALSE,
                scrollX = TRUE, scrollY = "400px"
              )
    )

```

## [Consumptions data]{style="color: #004F71; bold"}

```{r consumtab, echo = F}

datatable(params$consum, 
             
              class = "hover",
          rownames = FALSE,
              extensions = c("Buttons","FixedColumns"),
              options = list(
                dom = "Bt",
                buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span> Excel', title = NULL, 
                                    exportOptions = list(columns = ":visible"),
                                    filename =  paste("Consumptions_data"))
                ),
                paging=FALSE,
                searching = FALSE,
                ordering = FALSE,
                scrollX = TRUE, scrollY = "400px"
              )
    )

```

## [Occurrance data]{style="color: #004F71; bold"}

```{r ocdatatab, echo = F}

datatable(params$ocdata, 
            
              class = "hover",
          rownames = FALSE,
              extensions = c("Buttons","FixedColumns"),
              options = list(
                dom = "Bt",
                buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span> Excel', title = NULL, 
                                    exportOptions = list(columns = ":visible"),
                                    filename =  paste("Occurrance_data"))
                ),
                paging=FALSE,
                searching = FALSE,
                ordering = FALSE,
                scrollX = TRUE, scrollY = "400px"
              )
    )

```

## [Prevalence data]{style="color: #004F71; bold"}

```{r prevdatatab, echo = F}

datatable(params$prevdata, 
             
              class = "hover",
          rownames = FALSE,
              extensions = c("Buttons","FixedColumns"),
              options = list(
                dom = "Bt",
                buttons = list(list(extend = "excel", text = '<span class="glyphicon glyphicon-download-alt"></span> Excel', title = NULL, 
                                    exportOptions = list(columns = ":visible"),
                                    filename =  paste("Prevalence_data"))
                ),
                paging=FALSE,
                searching = FALSE,
                ordering = FALSE,
                scrollX = TRUE, scrollY = "400px"
              )
    )

```

<br>
